Fossil-calibrated phylogeny of Onagraceae: patterns of floral and chromosome evolution

### 2014-04-26 manuscript.tex
new figures and stuff

\title{Fossil-calibrated phylogeny and chromosome evolution of Onagraceae}

@@

@@

@@

\begin{figure*}[t]
    \centering
    % have to trim bottom off image
    \includegraphics[width=1.0\textwidth, trim=0 10 0 0, clip=true]{colored_posterior}
    \caption{Phylogeny blah blah blah}
    \label{posteriors}
\end{figure*}

\begin{figure*}[t]
    \centering
    % have to trim bottom off image
    \includegraphics[width=1.0\textwidth, trim=0 10 0 0, clip=true]{time_colored_genera}
    \caption{Phylogeny blah blah blah}
    \label{genera}
\end{figure*}

>>>>

\title{Fossil-calibrated phylogeny of Onagraceae: patterns of floral and chromosome evolution}

@@

Here is a table of the fossil calibrations used....

@@

Here is a table with the mean divergence time estimates including \%95 confidence intervals....

@@

\begin{figure*}[p]
    \vspace*{-2cm}
    \makebox[\linewidth]{
        % have to trim bottom off image
        \includegraphics[width=1.6\linewidth, trim=0 10 0 0, clip=true]{colored_posterior}
    }
    \caption{Phylogeny blah blah blah}
    \label{posteriors}
\end{figure*}

\begin{figure*}[p]
    \vspace*{-2cm}
    \makebox[\linewidth]{
        \includegraphics[width=1.6\linewidth, trim=0 10 0 0, clip=true]{time_colored_genera}
    }
    \caption{Sequence diagram}
    \label{genera}
\end{figure*}
